\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2014-12-05 Proposal.tex
more work

The intention behind the Semantic Web \cite{BernersLee:tsw98} is to transform the World Wide Web (WWW) from a web of mere human readable information to an information web with relations between different resources. There are interesting similar developments in other fields such as that of new presentation tools. These aim to enable the presentation of information in a more interconnected way that provides context. Both developments strive to connect pieces of information through providing context, to not just provide information, but rather knowledge.\\

@@

One can define knowledge as "the information necessary to support intelligent reasoning." \cite{Kohlhase:Complog:base} That said, it is imperative to facilitate knowledge transfer. Figure \ref{fig:dataknow} (based on \cite{ProbstRaubRomhardt} and \cite{Kohlhase:Complog:base}) shows the path from mere data to knowledge, through adding context, such that we gain information. From information, we can obtain knowledge through adding networking.\\

@@

To exemplify this: Annie, a young student learning mathematics, is watching her teacher give a presentation on how to use the Pythagorean theorem (see figure \ref{fig:Annie-presentation-teacher}). She is given a triangle with sides a = 3 cm and b = 4 cm. Now she wants to use the theorem to calculate the length of side c. Annie already knows how to calculate the square of a number and thus calculates that $c^2 = 25 \implies c = 5$. However Annie made a mistake and did not know what a right triangle is. Her teacher tells her that the question was a trick question and that the answer is wrong because the triangle she calculated this for is not a right triangle. Now Annie has to try to find out what a right triangle is. This shows the dependencies of different pieces of information (see figure \ref{fig:Annie-presentation-information}), i.e. the Pythagorean theorem depends on knowledge of squares,triangles, lengths, area calculation, and right angles. In an ideal presentation this information should have been linked to the current piece of information so that Annie could have directly looked it up instead of having to search for it.\\

@@

\begin{wrapfigure}{l}{0.6\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.55\textwidth]{assets/Annie4xml3}
    }
  \end{center}
\vspace{-20pt}
  \caption{Narrative Layers and semantic closeness}
  \label{fig:Annie-semantic-closeness}
\vspace{-10pt}
\end{wrapfigure}

In \textit{A mathematical approach to ontology authoring and
documentation} \cite{LK:MathOntoAuthDoc09}, it is stated that "documents consist of narrative and content layers". In our case, the content layers are the mathematical objects, i.e. the statements or theories. Narrative layers refer to the order the mathematical objects from content layers are presented. In figure \ref{fig:Annie-semantic-closeness}, this temporal information is represented through the arrows that connect the topics as the lecturer intends to teach them. Through the annotations within the document, we can establish levels of semantic closeness for different mathematical objects. These levels of semantic closeness are represented through the different sizes of the frames of the related information. In the proposed research the mathematical knowledge will be processed and visualized in a way that enables students to learn more efficiently through combining spatial narrative and semantic closeness. Thus it will not only provide the information or provide a narrative but it will provide a more interactive approach to presentations and learning.\\

@@

Going back to the example of Annie, the information about the Pythagorean theorem that the teacher is just introducing would be considered \textit{course-new}. The information about the right angle which Annie cannot access anymore since she was taught about this too long ago is \textit{course-ancient}. This is marked orange in figure \ref{fig:Annie-ancient}. The information about squares which Annie still remembers is \textit{course-old}. Through the semantic closeness that OMDoc provides us we will be able to determine the status of information within the (dis)course. \\

@@

In the proposed research we will focus less on text, tree-like structures, metaphors, or semiotics, like the sign of a woman on a door. We will rather focus on the spatial narrative and placing content that is inherently related visually close together since this can convey the meaning that these objects belong together.\\

@@

Figure \ref{fig:Objects} above clarifies what we mean by 'meaningful representations'. Figure \ref{fig:imp_objects} shows how size conveys importance. It is well known that people tend to identify the circle on the right as most important, the ones on the left are less important due to their relative size. Considering the relation of the three circles most people say that the two circles on the left belong together whereas the circle on the right is clearly something different. When shown Figure \ref{fig:rel_objects} they quickly change their mind and say that they are now actually related.\\
\newpage
\begin{wrapfigure}{l}{0.5\textwidth}
\vspace{-10pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.45\textwidth]{assets/Annie4size}
    }
  \end{center}
\vspace{-20pt}
  \caption{Relative size and relations} 
  \label{fig:Annie-relsize}
\vspace{-10pt}
\end{wrapfigure}

These perceptions can be used to convey meaning visually. For the example of Annie this means that the \textit{course-new} information would likely be important and therefore bigger than the \textit{content-old} or \textit{content-ancient} information. Then, it depends on how important the topics related to this topic are and we will use different sizes to differentiate between more important and less important topics. Similarly we will employ visual relations as in figure \ref{fig:rel_objects} to show related content. Considering figure \ref{fig:Annie-ancient}, we already have different sizes based on the relatedness of the concepts. Adding on to that in figure \ref{fig:Annie-relsize}, we have nodes that represent concepts that are very important for the course, here the next topic, represented as bigger. Thus we will provide Annie with a meaningful representation of the information taken from the information graph. In turn this should allow Annie to absorb information about importance and relations instinctively which improves knowledge transfer.\\

@@

For Impress.js, the primitive elements are text, images, slide-like structures (frames), and the visual relation between the different frame-like structures. The exact layout of the frames and the best visualization of the relation between the frames is to be determined. Ideally this should lead to Annie having the information about the Pythagorean theorem on a slide-like structure while having all the information the Pythagorean theorem depends on easily accessible so that she can reach \textit{course-old} information easily.  \ednote {not sure whether I understand this correctly - does this need more explanation?}
\ednote {visual and graph language have different primitives and it's interesting how it is mapped to one another}

>>>>

The intention behind the Semantic Web \cite{BernersLee:tsw98} is to transform the World Wide Web (WWW) from a web of mere human readable information to an information web with relations between different resources. There are interesting similar developments in other fields such as that of new presentation tools. These aim to enable the presentation of information in a more interconnected way that provides context. Both developments strive to connect pieces of information through adding context, to not just provide information, but rather knowledge.\\

@@

One can define knowledge as "the information necessary to support intelligent reasoning." \cite{Kohlhase:Complog:base} That said, it is imperative to facilitate knowledge transfer. Figure \ref{fig:dataknow} (based on \cite{ProbstRaubRomhardt} and \cite{Kohlhase:Complog:base}) shows the path from mere data to knowledge, through adding context, such that we gain information. From information, we can then obtain knowledge through adding networking.\\

@@

To exemplify this: Annie, a young student learning mathematics, is watching her teacher give a presentation on how to use the Pythagorean theorem (see figure \ref{fig:Annie-presentation-teacher}). She is given a triangle with sides a = 3 cm and b = 4 cm. Now she wants to use the theorem to calculate the length of side c. Annie already knows how to calculate the square of a number and thus calculates that $c^2 = 25 \implies c = 5$. However Annie made a mistake and did not know what a right triangle is. Her teacher tells her that the question was a trick question and that the answer is wrong because the triangle she calculated this for is not a right triangle. Now Annie has to try to find out what a right triangle is. This shows the dependencies of different pieces of information (see figure \ref{fig:Annie-presentation-information}), i.e. the Pythagorean theorem depends on knowledge of squares, triangles, lengths, area calculation, and right angles. In an ideal presentation this information should have been linked to the current piece of information so that Annie could have directly looked it up instead of having to search for it.\\

@@

\begin{wrapfigure}{l}{0.6\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.58\textwidth]{assets/Annie4xml3}
    }
  \end{center}
\vspace{-20pt}
  \caption{Narrative Layers and semantic closeness}
  \label{fig:Annie-semantic-closeness}
\vspace{-10pt}
\end{wrapfigure}

In \textit{A mathematical approach to ontology authoring and
documentation} \cite{LK:MathOntoAuthDoc09}, it is stated that "documents consist of narrative and content layers". In our case, the content layers are the mathematical objects, i.e. the statements or theories. Narrative layers refer to the order the mathematical objects from content layers are presented. In figure \ref{fig:Annie-semantic-closeness}, this temporal information is represented through the arrows that connect the topics as the lecturer intends to teach them. Through the annotations within the document, we can establish levels of semantic closeness for different mathematical objects. These levels of semantic closeness are represented through the different sizes of the frames of the related information. In the proposed research the mathematical knowledge will be processed and visualized in a way that enables students to learn more efficiently through combining spatial narrative and semantic closeness of content. Thus it will not only provide the information or provide a narrative but it will provide a more interactive approach to presentations and learning.\\

@@

Going back to the example of Annie, the information about the Pythagorean theorem that the teacher is just introducing would be considered \textit{course-new}. The information about the right angle which Annie cannot access anymore since she was taught about this too long ago is \textit{course-ancient}. This is marked orange in figure \ref{fig:Annie-ancient}. The information about squares which Annie still remembers is \textit{course-old}. Through the semantic closeness that OMDoc provides, we will be able to determine the status of information within the (dis)course. \\

@@

In the proposed research we will focus less on text, tree-like structures, metaphors, or semiotics, like the sign of a woman on a door. We will rather focus on spatial narrative and placing content, that is inherently related, visually close together since this conveys the meaning that these objects belong together.\\

@@

Figure \ref{fig:Objects} above clarifies what we mean by meaningful representations. Figure \ref{fig:imp_objects} shows how size conveys importance. It is well known that people tend to identify the circle on the right as most important, the ones on the left are less important due to their relative size. Considering the relation of the three circles most people say that the two circles on the left belong together whereas the circle on the right is clearly something different. When shown Figure \ref{fig:rel_objects} they quickly change their mind and say that they are now actually related.\\
\newpage
\begin{wrapfigure}{l}{0.5\textwidth}
\vspace{-10pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.45\textwidth]{assets/Annie4size}
    }
  \end{center}
\vspace{-20pt}
  \caption{Relative size and relations} 
  \label{fig:Annie-relsize}
\vspace{-10pt}
\end{wrapfigure}

These perceptions can be used to convey meaning visually. For the example of Annie this means that the \textit{course-new} information would likely be important and therefore bigger than the \textit{content-old} or \textit{content-ancient} information. Then, it depends on how important the topics related to this topic are and we will use different sizes to differentiate between more important and less important topics. Similarly, we will employ visual relations as in figure \ref{fig:rel_objects} to show related content. Considering figure \ref{fig:Annie-ancient}, we already have different sizes based on the relatedness of the concepts. Adding on to that in figure \ref{fig:Annie-relsize}, we have nodes that represent concepts that are very important for the course, here the next topic, represented as bigger. Thus we will provide Annie with a meaningful representation of the information taken from the information graph. In turn this should allow Annie to absorb information about importance and relations instinctively which improves knowledge transfer.\\

@@

For Impress.js, the primitive elements are text, images, slide-like structures (frames), and the visual relation between the different frame-like structures. The exact layout of the frames and the best visualization of the relation between the frames is to be determined. Ideally this should lead to Annie having the information about the Pythagorean theorem on a slide-like structure while having all the information the Pythagorean theorem depends on easily accessible so that she can reach \textit{course-old} information easily. \\

Visual and normal tree-like graph language have different primitives and it is interesting how one can be mapped to the another. When we consider tree-like graphs, there are two structural primitives, namely the nodes/ concepts and the relations between nodes. Additionally we can add semantic primitives like attributes to the concepts and to the relations. These structural primitives and semantic primitives provide the basics that graphs can be built on.\\
